Summer 2025 ToDo

### 2025-06-02 Relations/Paper/Definitions.tex
More consistent proof environemnt. Update to UN->

\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gNP \iff \gNPe$
        \item $\gUN \implies \gUNto$
    \end{enumerate}
\end{proposition}
\begin{proof} \hfill
    \begin{enumerate}
        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| in \texttt{Implications.agda}.
        \item \verb|UN→UN→ : R isUN → R isUN→| in \texttt{Implications.agda}.
    \end{enumerate}
\end{proof}

The implication $\UNto \implies \UN$ does not hold, as can be seen in Example \ref{CE:un} in Subsection \ref{subsec:counterexamples}.

@@

The following is immediate.
\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gInc \implies \gRP$
        \item $\gRP \implies \gRPm$
    \end{enumerate}
\end{proposition}

It follows that every relation that is increasing in the sense of \terese
vacuously satisfies the RP condition.

We wanted to generalize $\RP$ and thought that with $\RPm$ we had a good candidate.
 We show that this weaker definition is
in fact equivalent in the following proof in \texttt{Implications.agda}:

\verb|RP-↔RP : R is RP- ↔ R is RP|.

>>>>

\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gNP \iff \gNPe$
        \item $\gUN \implies \gUNto$
    \end{enumerate}
\end{proposition}
\begin{proof} See\footnote{All proofs are formalized in the accompanying Agda code. References within the paper indicate the corresponding function names and their types to facilitate locating the relevant formalizations.} \hfill
    \begin{enumerate}
        \item \verb|NP₌↔NP : R isNP₌ ↔ R isNP| 
        \item \verb|UN→|\texttt{UN}$^{\to}$\verb|: R isUN → R is|\texttt{UN}$^{\to}$ \\ in \texttt{Implications.agda}.
    \end{enumerate}
\end{proof}

\begin{remark}
    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Subsection~\ref{subsec:counterexamples}.
\end{remark}

@@

\begin{proposition}\hfill
    \begin{enumerate}
        \item $\gInc \implies \gRP$
        \item $\gRP \iff \gRPm$
    \end{enumerate}
\end{proposition}

\begin{proof}
    See, \hfill
    \begin{enumerate}
        \item This is immediate.
        \item \verb|RP-↔RP : R isRP- ↔ (R isRP)|
    \end{enumerate}
    in \texttt{Implications.agda}
\end{proof}

%TODO: Update below to reflect new convenion for proofs and code.
\begin{remark}
    It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
\end{remark}

### 2025-06-02 Relations/Paper/Formalization.tex
Minor code update to reflect changes to wf.
More consistent proof environemnt. Update to UN->

\begin{proof}
    See, \\
    \verb|CR→NP : R isCR → R isNP₌|\\
    \verb|NP→UN : R isNP₌ → R isUN|\\
    \verb|ii : R isWN × R isUN → R isCR|\\
    \verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR|\\
    \verb|iii : subcommutative R → R isCR|\\
    in \texttt{Theorems.agda}.
\end{proof}
\begin{remark}
    In $\mathtt{UN→∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
\end{remark}

@@

There are four parts to this theorem. 
\begin{description}
    \item[($i$)] $\gWN \land \gUN \implies \gBP$
    \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
    \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
\end{description}
\begin{proof}
    See, \\
    \verb|i : R isWN → R isUN → R isBP|\\
    \verb|i→ : R isWN → R isUN→ → R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
    \verb|iv : R isCP → R isCR| \\
    in \texttt{Theroems.agda}.
\end{proof}

>>>>

\begin{proof}
    See, \\
    \verb|CR→NP : R isCR → R isNP₌|\\
    \verb|NP→UN : R isNP₌ → R isUN|\\
    \verb|ii : R isWN × R isUN → R isCR|\\
    \verb||\texttt{UN}$^{\to}$ \verb|∧WN→CR : R |\texttt{isUN}$^{\to}$ \verb| → R isWN → R isCR|\\
    \verb|iii : subcommutative R → R isCR|\\
    in \texttt{Theorems.agda}.
\end{proof}
\begin{remark}
    In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
\end{remark}

@@

There are four parts to this theorem. 
\begin{description}
    \item[($i$)] $\gWN \land \gUN \implies \gBP$
    \item[($ii$)] $\gBP \land \gInc \implies \gSN$  
    \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
\end{description}
\begin{proof}
    See, \\
    \verb|i : R isWN → R isUN → R isBP|\\
    \verb|i→ : R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
    \verb|iv : R isCP → R isCR| \\
    in \texttt{Theorems.agda}.
\end{proof}

### 2025-06-02 Relations/Paper/Summer_2025_TODO.tex
More consistent proof environemnt. Update to UN->

\documentclass{article}
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

@@

    \item (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.

@@

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit. 
  \item find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. 
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability. 
  \item Working on CR $\to$ CP. Low priority.  
\end{todolist}
\end{document}

>>>>

\documentclass{article}
\input{macros}
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

@@

    \item [\done] (we think) (Review 2) "l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.

@@

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit. 
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability. 
  \item Working on CR $\to$ CP. Low priority.  
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\ 
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to 
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$. 
  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons. 
\end{todolist}
\end{document}
